### 2017-09-08 paper/related.tex
pass

\section{Related Work}
\label{sec:related}
Researchers and practitioners have been shedding light to the demand
of techniques for optimizing test execution.

@@

\textit{Test Selection:} Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  \Fix{...} Most of these
techniques are unsoud (\ie{}, they do not guarantee that
fault-revealing tests will be selected), however, more recently, sound
techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}. Recent work
for test selection introduced
Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015} that conservatively
computes which tests have been impacted by file changes.  A test is
discarded for execution if it does not depend on any changed file
dynamically reachable from execution. Although Ekstazi is focused on
regression test selection, it highlights the importance of parallelism
as a complement to test selection.  In fact, as in their evaluation,
we also discovered subjects with parallelism enabled by default.  Test
suite parallelization is complementary to regression testing
techniques.

%% \textit{Usage of massively parallel hardware:}
\textit{Hardware level parallelization:} Previous research
investigated the feasibility of testing embedded software on Graphics
Processing Units (GPUs) as an alternative to multicore
CPUs~\cite{rajan-etal-ase2014}.  The Simple Instruction Multiple Data
(SIMD) architecture of modern GPUs allows running the same test case
with different test data over several threads.  Although benchmarks
indicate far superior performance over traditional multicore CPUs,
there are severe limitations. Control-flow branching in source code
can impact performance negatively while violating the lock-step
execution during the divergence of instructions~\cite{rajan-etal-ase2014}
%% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
%% language.
Recent work proposed a compiler-assisted approach to make programs
compatible with the relying programming-model used by
GPUs to parallelize tests~\cite{yaneva-etal-issta2017}.

\Jbc{...Justify they are out of scope for our subjects...}.

>>>>

\section{Related Work}
\label{sec:related}
We discuss most related work in the following.
%% Researchers and practitioners have been shedding light to the demand
%% of techniques for optimizing test execution.

@@

%\textit{Test selection:}
Regression testing research has focused
mostly on test suite minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012,soetens-etal-2016}.  Most of these
techniques are unsoud (\ie{}, they do not guarantee that
fault-revealing tests will be considered for testing).  The test
selection technique Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015}
is an example of a sound regression testing technique. It
conservatively computes which tests have been impacted by file
changes.  A test is discarded for execution if it does not depend on
any changed file dynamically reachable from execution.\Comment{ Curiously
Ekstazi's evaluation discovered subjects with parallelism enabled by
default.} \c{C}elik~\etal{}~\cite{celik-etal-fse2017} recently extended
Ekstazi to track files accessed outside JVM boundaries.  Important to
note that regression testing techniques, including test selection, is
complementary to test suite parallelization.

%\Luis{maybe we should create another division for test acceleration}

ElectricTest~\cite{bell-etal-esecfse2015} is a tool for efficiently
detecting data dependencies across test cases.  Dependency tracking is
important as to avoid test flakiness when parallelizing test
suites. ElectricTest observes reads and writes on global resources
made by tests to identify these dependencies at low cost. We remain to
investigate the impact of ElectricTest to reduce flakiness in
unrestricted test suite parallelization.

%% \textit{Usage of massively parallel hardware:}
%\textit{Hardware level massive parallelization:}

The use of the Simple Instruction Multiple Data (SIMD) design has been
previoulsy explored to accelerate test
execution~\cite{damorim-etal-issta2007,damorim-etal-tse2008,kim-etal-issre2012,nguyen-etal-icse2014,rajan-etal-ase2014,sen-etal-fse2015,yaneva-etal-issta2017}. The
SIMD architecture, as implemented in modern GPUs for instance, allows
the execution of a given instruction simultaneously against multiple
data.  For that reason, in principle, a test could be ran
simulteneously against multiple inputs.  Recent
work~\cite{rajan-etal-ase2014,yaneva-etal-issta2017} explored the
feasibility of testing embedded software using GPUs.  Although
benchmarks indicate superior performance compared to traditional
multicore CPUs, the use of the technology in broader settings is
unfortunately limited. For example, execution of more general programs
can violate SIMD's lock-step assumption on the control-flow of threads
affecting negatively performance. In contrast to the datasets used in
those papers, often each test is associated with a single input
(instead of many).  Furthermore, handling complex data is challenging
in SIMD~\cite{damorim-etal-issta2007,damorim-etal-tse2008}.

%% existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
%% language.
%% Recent work proposed a compiler-assisted approach to make programs
%% compatible with the relying programming-model used by
%% GPUs to parallelize tests~\cite{}.
%% \Jbc{...Justify they are out of scope for our subjects...}.

\Mar{can you complete this AND add text on high-level paralellism?}
